---
title: "p8105_hw1_jz4027"
author: "Charlotte Zhang"
date: "2025-09-17"
output: html_document
---

# Problem 1
```{r}
##Load needed library
library(ggplot2)
library(moderndive)
```
### Load dataset
```{r}
data("early_january_weather")
```
### Short description of the dataset
This dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.  
Variables include: `r paste(names(early_january_weather), collapse = ", ")`. 
The mean temperature is `r mean(early_january_weather$temp, na.rm = TRUE)` F.

### ggplot and ggsave
```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point() + labs(x = "Time_hour", y = "Temprature")
ggsave("p1_scatterplot.pdf", height = 4, width = 6)
```
### Patterns of the scatterplot
* The temperature has an overall increasing trend from early January to mid January
* Temperature increases during daytime and decreases at night, a repeating daily cycle. 
* The color of humidity is generally darker in early January (lower humidity), and lighter in mid January (higher humidity).


# Problem 2
```{r}
library(tidyverse)

# Create a data frame
p2_df = tibble(
  norm_samp = rnorm(10),
  log_vec = norm_samp > 0,
  char_vec = c("ab","cd","e","fgh","i","j","k","lmn","o","p"),
  factor_vec = factor(c("Level_1","Level_2","Level_3","Level_2","Level_2","Level_3","Level_1","Level_1","Level_2","Level_3"))
)

# Calculate the mean
mean_norm_samp = mean(pull(p2_df, norm_samp))
mean_log_vec = mean(pull(p2_df, log_vec))
mean_char_vec = mean(pull(p2_df, char_vec))
mean_factor_vec = mean(pull(p2_df, factor_vec))
``` 
* The mean of a random sample of size 10 from a standard Normal distribution is `r round(mean_norm_samp, digits = 2)`. The mean of a logical vector indicating whether elements of the sample are greater than 0 is `r round(mean_log_vec, digits = 2)`. The mean of a character vector of length 10 is `r mean_char_vec`. The mean of a factor vector of length 10, with 3 different factor “levels” is `r mean_char_vec`.
* The first two works because they are numeric variables (Logic vector: TRUE=1, FALSE=0). The last two do not work because they are character and factor variables. 

