---
title: "p8105_hw1_jz4027"
author: "Charlotte Zhang"
date: "2025-09-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 1
##Load needed library
```{r setup, include = FALSE}
library(ggplot2)
library(moderndive)
```
## Load dataset
```{r}
data("early_january_weather")
```
## short description of the dataset
This dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.  
Variables include: `r paste(names(early_january_weather), collapse = ", ")`. 
The mean temperature is `r mean(early_january_weather$temp, na.rm = TRUE)` °F.
## ggplot and ggsave
```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point() + labs(x = "Time_hour", y = "Temprature")
ggsave("p1_scatterplot.pdf", height = 4, width = 6)
```
## Patterns of the scatterplot
* The temperature has an overall increasing trend from early January to mid January
* Temperature increases during daytime and decreases at night, a repeating daily cycle. 
* The color of humidity is generally darker in early January (lower humidity), and lighter in mid January (higher humidity).  
